Delayed effects of climate on vital rates leads to demographic divergence in Amazonian forest fragments

### 2021-06-17 doc/paper.Rmd
add 95%ci to results for flowering

Overall, the the probability of flowering was higher in continuous forest than in 1-ha fragments for all values of SPEI (Figure \@ref(fig:flwr-spei)).
The responses in 1-ha fragments were also more muted (1-ha edf = 8.3, continuous forest edf = 10.6), as indicated by the shape of the crossbasis function (Figure \@ref(fig:flwr-spei)a).
This led to some important inter-habitat differences in plant responses to prior droughts.
Recent drought (i.e., at lag = 0 with SPEI \< -1) increased the probability of flowering in continuous forest, as did drought at lags 15--20 (i.e., two dry seasons prior).
However, drought at lags 7--13 (the end of the rainy season one year prior) reduced flowering probability in continuous forest far more than it did in fragments (Figure \@ref(fig:flwr-spei)c).

Finally, with the exception of survival in 1-ha fragments ($p = 0.253$), the delayed effects of SPEI on all three vital rates varied significantly among plots ($p < 0.01$ for the random effect of plot).
We found no evidence for a cost of reproduction.
In both forest and fragments, flowering in the previous year was significantly positively related to growth (CF: $p = 0.048$; 1-ha: $p = 0.030$) and flowering (CF: $p < 0.001$; 1-ha: $p = 0.004$) meaning that plants which had flowered in the previous year were more likely to be larger and flower again, on average.
The random effect of plant ID was also significant for flowering probability (CF: $p < 0.001$; 1-ha: $p=0.003$) indicating significant individual-level variation in flowering probability.

>>>>

Overall, the the probability of flowering was higher in continuous forest than in 1-ha fragments for all values of SPEI (Figure \@ref(fig:flwr-spei)), although this difference was not significant (84% CI of intercepts overlaps).
The responses in 1-ha fragments were also more muted as indicated by the shape of the crossbasis function (1-ha edf = 8.3, continuous forest edf = 10.6) (Figure \@ref(fig:flwr-spei)).
This led to some important inter-habitat differences in plant responses to prior droughts.
In continuous forests, recent drought (i.e., at lag = 0--2 with SPEI \< -1), drought two dry seasons prior (lags 15--20 ) and in the wet season 34--36 months prior all increased the probability of flowering.
However, drought at the end of the rainy season one year prior (lags 7--13) significantly reduced flowering probability (Figure \@ref(fig:flwr-spei)a).
In Fragments, recent drought had no significant effect on flowering probability and only drought at two dry seasons prior (lags 16--20) and in the wet season 33--36 months prior increased flowering probability (Figure \@ref(fig:flwr-spei)b).
The effects of drought on flowering probability were strong in continuous forest compared to 1 ha fragments (Figure \@ref(fig:flwr-spei)c).

Finally, with the exception of survival in 1-ha fragments ($p = 0.253$), the delayed effects of SPEI on all three vital rates varied significantly among plots ($p < 0.01$ for the random effect of plot).
We found no evidence for a cost of reproduction: in both forest and fragments, flowering in the previous year was significantly positively related to growth (CF: $p = 0.048$; 1-ha: $p = 0.030$) and flowering (CF: $p < 0.001$; 1-ha: $p = 0.004$) meaning that plants which had flowered in the previous year were more likely to be larger and flower again, on average.
The random effect of plant ID was also significant for flowering probability (CF: $p < 0.001$; 1-ha: $p=0.003$) indicating significant individual-level variation in flowering probability.
